%netscout - technical paper
%author - Aditya Joshi
\documentstyle[twocolumn]{article}
\pagestyle{empty}
%set dimensions of columns, gap between columns, and paragraph indent 
\setlength{\textheight}{8.75in}
\setlength{\columnsep}{2.0pc}
\setlength{\textwidth}{6.8in}
\setlength{\footheight}{0.0in}
\setlength{\topmargin}{0.0in}
\setlength{\headheight}{0.0in}
\setlength{\headsep}{0.0in}
\setlength{\oddsidemargin}{-.19in}
\setlength{\parindent}{1pc}
\makeatletter
\def\@normalsize{\@setsize\normalsize{10pt}\xpt\@xpt
\abovedisplayskip 10pt plus2pt minus5pt\belowdisplayskip 
\abovedisplayskip \abovedisplayshortskip \z@ 
plus3pt\belowdisplayshortskip 6pt plus3pt 
minus3pt\let\@listi\@listI}
%need an 11 pt font size for subsection and abstract headings 
\def\subsize{\@setsize\subsize{12pt}\xipt\@xipt}
%make section titles bold and 12 point, 2 blank lines before, 1 after 
\def\section{\@startsection {section}{1}{\z@}{1.0ex plus 1ex minus .2ex}{.2ex plus .2ex}{\large\bf}}
%make subsection titles bold and 11 point, 1 blank line  before, 1 after 
\def\subsection{\@startsection {subsection}{2}{\z@}{.2ex plus 1ex} {.2ex plus .2ex}{\subsize\bf}}
\makeatother

\begin{document}
%don't want date printed
\date{}
%make title bold and 14 pt font (Latex default is non-bold, 16pt) 
\title{\Large\bf netscout - adaptive network monitoring and countering mechanism}
%for single author (just remove % characters)
%\author{I. M. Author \\
%  My Department \\
%  My Institute \\
%  My City, STATE, zip}
%for two authors (this is what is printed) 
\author{\begin{tabular}[t]{c@{\extracolsep{8em}}c} 
Aditya Joshi  & G Sivakumar \\
 \\
        Research Advisee & Professor \\
        Computer Science and Engineering & Computer Science and Engineering \\
        IIT Bombay, Mumbai - 400076 & IIT Bombay, Mumbai - 400076
\end{tabular}}
\maketitle
%I don't know why I have to reset thispagestyle, but otherwise get page numbers 
\thispagestyle{empty}
\subsection*{\centering Abstract}
%IEEE allows italicized abstract
{\em
Networks often contain logging information in diverse files and formats. 
In order to get a complete logical picture of network activity, monitoring 
various applications and protocols is required. netscout aims to provide
a logical level of control to users in order to monitor, filter and counter
policy violating network activity.
%end italics mode
}
\section{Introduction}
Here is my introduction text.  There are 2 blank lines 
before the section heading and one afterwards.  Heading 
text is 12 point bold font.  Paragraphs are not indented. 
I may want a numbered subsection, which is done as 
follows.
\subsection{Previous Work}
In subsections there is 1 blank line before the section 
heading and one afterwards.  Heading text is 11 point 
bold font.  Paragraphs are indented one pica.  There is 
no blank line between paragraphs.
Throughout I may cite references of the form 
\cite{key:foo} or \cite{foo:baz}, and LaTeX will keep 
track of numbering.  The numbers are based on the order 
you place them in the bibliography, not the order they 
appear in the text.  They should (I believe) be in 
alphabetical order.  LaTex will put square brackets about 
the number within the text of your paper.  For those of 
you new to the bibliography package, you may have to run 
the latex process twice to allow all references to be 
resolved. You will get a warning about a missing .aux 
file.  Just rerun latex and it will be ok.
\section{}
\section{Summary and Conclusions}
This template will get you through the minimum article, 
i.e. no figures or equations.  To include those, please 
refer to your LaTeX manual and the IEEE publications 
guidelines.  Good Luck!
%this is how to do an unnumbered subsection
\subsection*{Acknowledgments}
This is how to do an unnumbered subsection, which comes 
out in 11 point bold font.  Here I thank my colleagues, 
especially Mike Gennert, who know more about Tex and 
Latex than I.
\begin{thebibliography}{9}
\bibitem{key:foo}
I. M. Author,
``Some Related Article I Wrote,''
{\em Some Fine Journal}, Vol. 17, pp. 1-100, 1987.
\bibitem{foo:baz}
A. N. Expert,
{\em A Book He Wrote,}
His Publisher, 1989.
\end{thebibliography}
\end{document}


